Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-07 paper.tex
commenting some TODOs and CONCERNs

%********************************************************************************
\section{State of the art on sales forecasting} 
\label{sec:soa}
% Antonio - TODO: Since two new sections have been added here, maybe we should change the title of the section... Maybe 'Background and related works'?

@@

% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
% Antonio - CONCERN - should we change the term 'classification' by 'regression' somehow?

@@

%In classification problems the algorithm searches for an optimal hyperplane 
%that separates two classes, maximising the margin between them.
% Antonio - CONCERN - remove this classification thing due to a reviewer's comment 
In regression problems, the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.
% Antonio - CONCERN - something about regression?

@@

% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before. And rewrite the initial paragraphs to separate it from section 4 (methodology)

@@

% previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
% Antonio - TODO - revise them

@@

In this stage, both numerical and visualisation-based approaches have been 
applied, in order to select the best variables for the forecasting methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Could they be used with the same meaning?

% Antonio - TODO: The next paragraph is referring to Section 2.1. We must change it.
In Section \ref{subsec:select_method}, a selection of the best forecasting techniques that have been conducted has been reported, looking for those rule- or tree-based, together with numerical methods which could yield the best results.

@@

% Antonio - a better description of U-Matrix. ;D

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold). Just the features selected by ReliefFAttributeEval method have been considered.}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)

@@

% Antonio - I have reordered the tables correctly. ;D

>>>>

%********************************************************************************
\section{State of the art on sales forecasting} 
\label{sec:soa}
% Antonio - TODO: Since two new sections have been added here, maybe we should change the title of the section... Maybe 'Background and related works'?
% I don't see how or what the new title might change ....  ???   we can discuss this item later this morning.

@@

% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before.
Many of the previous papers propose using different prediction methods.
Thus, next subsections describe several forecasting methods and different 
evaluation criteria, commonly used in the bibliography that have been chosen 
to face the problem at hand.

@@

 % weka.classifiers.lazy.IBk 
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/lazy/IBk.html
 \item \emph{k-Nearest Neighbours (kNN)}: 
The kNN \cite{Aha1991,Mitchell1997} method is an instance-based classifier in 
which the unknown instances are classified by relating them to the known 
instances using a distance measurement/function: Euclidean, Minkowsky or minimax.
% Antonio - CONCERN - should we change the term 'classification' by 'regression' somehow?
% I don't think so in this case. That is what kNN is...

@@

%In classification problems the algorithm searches for an optimal hyperplane 
%that separates two classes, maximising the margin between them.
% Antonio - CONCERN - remove this classification thing due to a reviewer's comment 
% ok    :)
In regression problems, the algorithm chooses a hyperplane close to as many 
of the data points as possible, minimising the sum of the distances from 
the data points to the hyperplane. 
In both cases, the hyperplane is defined by a subset of training set samples, 
called support vectors.
%This method works well even if the space is highly dimensional and the problem is not linearly separable.

 % weka.classifiers.functions.MultilayerPerceptron
 %		http://weka.sourceforge.net/doc.dev/weka/classifiers/functions/MultilayerPerceptron.html
 \item \emph{Multilayer Perceptron}:
A Multilayer Perceptron (MLP) \cite{Rosenblatt1962,Widrow1990} is a feedforward 
artificial neural network model that maps the input data onto an appropriate output. 
It is an artificial neural network generally used for classification or 
approximation problems.
% Antonio - CONCERN - something about regression?
% in that sentence, approximation is used as synonymous of regression   ;)

@@

% Antonio - TODO: link this section with the rest of the SotA. Introduce it in a paragraph before. And rewrite the initial paragraphs to separate it from section 4 (methodology)
% I have addressed this "todo" before (lin. 353)

@@

% previous two sub-sections have been moved here as requested by reviewer #3 in comment #2 (issue #47)
% Antonio - TODO - revise them
% What have to be revised?   :/

@@

In this stage, both numerical and visualisation-based approaches have been 
applied, in order to select the best variables for the forecasting methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Could they be used with the same meaning?
% I think so.

% Antonio - TODO: The next paragraph is referring to Section 2.1. We must change it.
% Why? anyway, I add "As stated before,"
As stated before, in Section \ref{subsec:select_method} a selection of the best 
forecasting techniques that have been conducted has been reported, looking for 
those rule- or tree-based, together with numerical methods which could yield 
the best results.

@@

% Antonio - a better description of U-Matrix. ;D
% thanks!

@@

\begin{figure*}[ht]
\begin{center}
\includegraphics[scale=0.6]{./imgs/attribute_All.eps}
\end{center}
\caption{Boxplots showing the values obtained predicting \texttt{total\_sales} with different regression methods (30 repetitions, 10-fold cross validation). Results obtained for different special publishing companies: UDL929 (the best selling publishing company), UDLW12 (the median selling publishing company), UDL704 (highest number of different titles sold) and UDLU11 (medium number of different books sold). Just the features selected by ReliefFAttributeEval method have been considered.}
\label{fig:attributeAll}
\end{figure*}
% Antonio - CONCERN - The text and the results must be contrasted. If I'm not wrong, I remember that we decided to include here just the results obtained by ReliefFAttributeEval, since they were quite good (maybe the best). But there are plotted apparently the results for all the features. Anyway, in the text, it is said that the process is using all the features, then apply FS. But here just the results for all the features are shown. Why don't we show also the results for the corresponding sets of features selected by each FS method?
% Actually in the previous version there were several tables with these results than have been moved to the Appendix. I think we should include another figure fro them. They show important information. ;)
% we can discuss this point later this morning. If necessary, we can design and include a new plot.

@@

% Antonio - I have reordered the tables correctly. ;D
% thanks!!! (again)
